---
title: "LinearM"
author: "CainaGuardado"
date: "10/29/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)
require(tidyverse)
require(tigerstats)
```

# Introduction

 Form  THE three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 
 
 
# SIMS~ARM REGRESSION 

```{r}
plot(SIMS~ARM,data=data)
```

```{r}
basicNN <- ggplot(data,aes(y=SIMS,x=ARM))
```


```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

```{r}
basicNN +geom_point()+ geom_smooth(method=lm)
``` 

The greater the ARM force ,the greater the SIMS score increase meaning the correlate together which the scatter plot looks like a  linear  is trending up which is a sign a for a postive correlated data.The shaded part is the uncertainity of the blue line .



```{r}
cor(SIMS~ARM,data=data)
```

0.686 is a positive correlation between SIMS score and ARM FORCE Correlations is the measure of the linear associates.

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```

The equations is SIMS is lm(formula = SIMS ~ ARM, data = data);
SIMS= -4.095160 + 0.054563  * ARM 

```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval = "prediction")
```
Fit is the predicted ARM score when you have a grip score of 94 and the ARM strength of 88.
 Lwr and Upr are the 95% confidence intervals for prediction when GRIP is 94 and ARM is 88.
 
 


# SIMS~GRIP REGRESSION  

```{r}
plot(SIMS~GRIP,data=data)
```

The greater the GRIP force ,the greater the SIMS score increase meaning that they  correlate together which the scatter plot looks like a postive slope  which is trending up which is a sign a for a postive correlation.




```{r}
cor(SIMS~GRIP,data=data)
```

0.6398 is a positive correlation because the number is psotive not negative or above one  between SIMS score and GRIP FORCE .

```{r}
basicNN +geom_point()+ geom_smooth(method=lm)
``` 

```{r}
model.1 <- lm(SIMS~GRIP,data=data)
summary.lm(model.1)
```

The equations is SIMS is lm(formula = SIMS ~ GRIP, data = data);
SIMS= -4.809675 +  0.045463 * GRIP



```{r}
newData=data.frame(GRIP=94,ARM=88)
predict.lm(model.1,newData,interval = "prediction")
```

Fit is the predicted SIM score when you have a GRIP strength of 94.
lwr and upr are 95% confidence intervals for predicted SIMS score when the GRIP score  is 94 .

Comparing both models1 and 2 it shows that Model1 (SIM~ARM) has a slight smaller residual standred error score of 1.226 unlike model 2(SIMS ~GRIP) score slightly higer of 1.295.Model 1has a higher R squared of 0.467 while model 2 is lower 0.4053
 
 Model 1 appears to be a slightly better model because it has a lower residual and higher R square score.


# SIMS~ARM+GRIP  
```{r}
plot(SIMS~ARM+GRIP,data=data)
```



```{r}
model.1 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.1)
```

```{r}
cor(SIMS~ARM+GRIP,data=data)
```


```{r}
model.1 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.1)
```


# MODEL COMPARISONS  



